Benchmark!!1

### 2020-12-23 paper/main.tex
lns benchmark implementations: C++ (all except static), Java (all except static), Javascript
new note on data structures for Labels in Python

\section{Considered benchmarks and their format}

@@

>>>>

\section{Considered benchmarks and their format}
\subsection{2-opt}
\subsection{Or-opt}
\subsection{Large neighbourhood search}

Note: we use a vector and not a set to store unplanned requests,
otherwise we take the risk of losing determinism.

\subsection{Something DP-like}

@@

\section{Other notes}
On the ESPPRC benchmark, a label needs to store information about
which customers have already been visited in the partial path it
represents. In Python, preliminary testing reveals that using a set of
integers for that purpose is twice as fast as using a vector of booleans.
